О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
with side length -> of side length

\begin{lemma}
	\cite[Lemma 4]{our-vmmsh-2018}
	\label{lem:square_container}
	Let $M\in\mathfrak{M}(2,n)$, $\operatorname{diam} M = d$.
	Then $M$ is situated in a square with side length $d$.
\end{lemma}

@@

\begin{proof}
	For $4 \leq n \leq 21491$, the claim of the theorem follows immediately from Observation~\ref{obs:4_leq_n_leq_21491}.
	Let us consider $M\in \mathfrak{M}(2,n)$, $n \geq 21492$, $\operatorname{diam} M = b$.
	Lemma~\ref{lem:square_container} yields that $M$ is situated in a square with side length $b$.
	Let $M_1, M_2, M_3, M_4$ be points of $M$ such that the distances $|M_1 M_2|$ and $|M_3 M_4|$
	are minimal in $M$ ($M_2$ and $M_3$ may be the same point).
	Then $|M_1 M_2| \leq b\varphi_{n-1}$ and $|M_3 M_4| \leq b\varphi_{n-1}$.
	Due to Lemma~\ref{lemma:quadr_diag_edges}, open line segments $M_1 M_2$ and $M_3 M_4$ do not intersect
	(otherwise they are not minimal).

@@

\begin{remark}
	Applying Construction~\ref{con:planar_set_with_minimeter_1} to $k=1$ naively,
	we get $a = 3$, $I=\varnothing$, $b_\varnothing = -1$ and then
	obtain a right triangle with side length 1.
	This triangle is obviously the optimal set in $\mathfrak{M}(2,3)$.
\end{remark}

@@

For $m \geq 3$, Conjecture~\ref{hyp:prime_planar} can be easily proved:
indeed, we can just take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex with proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all points $M_J$, except the two points with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is prime.

>>>>

\begin{lemma}
	\cite[Lemma 4]{our-vmmsh-2018}
	\label{lem:square_container}
	Let $M\in\mathfrak{M}(2,n)$, $\operatorname{diam} M = d$.
	Then $M$ is situated in a square of side length $d$.
\end{lemma}

@@

\begin{proof}
	For $4 \leq n \leq 21491$, the claim of the theorem follows immediately from Observation~\ref{obs:4_leq_n_leq_21491}.
	Let us consider $M\in \mathfrak{M}(2,n)$, $n \geq 21492$, $\operatorname{diam} M = b$.
	Lemma~\ref{lem:square_container} yields that $M$ is situated in a square of side length $b$.
	Let $M_1, M_2, M_3, M_4$ be points of $M$ such that the distances $|M_1 M_2|$ and $|M_3 M_4|$
	are minimal in $M$ ($M_2$ and $M_3$ may be the same point).
	Then $|M_1 M_2| \leq b\varphi_{n-1}$ and $|M_3 M_4| \leq b\varphi_{n-1}$.
	Due to Lemma~\ref{lemma:quadr_diag_edges}, open line segments $M_1 M_2$ and $M_3 M_4$ do not intersect
	(otherwise they are not minimal).

@@

\begin{remark}
	Applying Construction~\ref{con:planar_set_with_minimeter_1} to $k=1$ naively,
	we get $a = 3$, $I=\varnothing$, $b_\varnothing = -1$ and then
	obtain a right triangle of side length 1.
	This triangle is obviously the optimal set in $\mathfrak{M}(2,3)$.
\end{remark}

@@

For $m \geq 3$, Conjecture~\ref{hyp:prime_planar} can be easily proved:
indeed, we can just take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex of proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all points $M_J$, except the two points with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is prime.
